
\documentclass{amsart}

\input{../preamble.tex}

\usepackage{marginnote}

\begin{document}

\noindent\textbf{Claim:} the iterated integral map
\begin{equation*}
    \sigma: CC_*(\Omega^*(M)) \to \Omega^*(LM)
\end{equation*}
on differential forms is a map of graded vector spaces, but 
checking that it is a map of chain complexes uses the (graded) commutativity of 
differential forms. We will sketch this below.

The reason I want to emphasize this point is because
the analogous iterated integral map for (\v Cech-)Deligne cocycles will not be
a map of chain complexes. Since the Beilinson-Deligne cup product is commutative
up to homotopy, we will instead get $\sigma\circ b = d\circ\sigma + d\circ h$
for some term $h$. So we still obtain a map on cohomologies but not a map of 
chain complexes. This is problematic because the usual tools of spectral 
sequences etc rely on having a map of chain complexes (or perhaps this notion of 
up-to-exact-term chain map is enough?).

%The product structure on the Deligne complex is rather 
%subtle (it is not a dg algebra but a graded algebra in complexes $\oplus_p
%\Z_d(p)$) so this is just an educated guess for now. I will try to work it out 
%more carefully.

\hrulefill \\

Let $M$ be a (simply connected) manifold.
We denote by $CC_*(-)$ the Hochschild chain complex of a dg algebra.
We define a map
\begin{equation*}
    \sigma: CC_*(\Omega^*(M))=\bigoplus_{k=0}^\infty \Omega^*(M)^{\otimes k} \to 
    \Omega^*(LM)
\end{equation*}
as follows. Let
\begin{equation*}
    \omega_0\otimes \cdots \otimes \omega_k \in CC_k(\Omega^*(M)) = 
    \Omega^*(M)^{\otimes k}.
\end{equation*}
Using the projection maps $p_j: M^{k+1}\to M$, we obtain
\begin{equation*}
    p_0^*\omega_0 \wedge \cdots p_k^*\omega_k \in \Omega^*(M^{k+1}).
\end{equation*}
We transgress this form along the diagram:
\begin{equation*}
    \begin{tikzcd}
        \Delta^k \times LM \rar{ev_k}\dar{\pi} & M^{k+1} \\
        LM
    \end{tikzcd}
\end{equation*}
where
\begin{align*}
    ev_k : \Delta^k \times LM &\to M^{k+1} \\
    (t_1,\ldots, t_k, \ell) &\mapsto (\ell(0),\ell(t_1),\ldots,\ell(t_k)).
\end{align*}
So we obtain
\begin{equation*}
    \sigma(\omega_0\otimes\cdots\otimes\omega_k) =
    \pi_!ev_k^*(p_0^*\omega_0\wedge\cdots\wedge p_k^*\omega_k) \in \Omega^*(LM).
\end{equation*}
Under a suitable grading of the Hochschild complex (see Getzler-Jones-Petrack) 
this map extends to a map $\sigma$ of graded vector spaces.

Let us check that $\sigma$ is a map of chain complexes, i.e. that
\begin{equation}
    \sigma \circ b = d \circ \sigma,
    \label{chainmap}
\end{equation}
where
\begin{align}
    b(\omega_0\otimes \cdots \otimes \omega_k) &=
    \sum_{j=0}^k \pm \omega_0\otimes\cdots \otimes
    d\omega_j \otimes \cdots \omega_k \label{l1}\\
    &+ \sum_{j=0}^{k-1} \pm \omega_0\otimes \cdots\otimes
    (\omega_j\wedge\omega_{j+1}) \otimes \cdots \otimes \omega_k \label{l2} \\
    & \pm \omega_k\wedge\omega_0\otimes\omega_1\otimes \cdots\otimes 
    \omega_{k-1}\label{l3}
\end{align}
is the Hochschild differential. We can already see where commutativity of 
differential forms will be necessary: on the left hand side of 
eq.~\ref{chainmap} we have a term that looks like
$\sigma(\omega_k\wedge\omega_0\otimes \cdots)$ whereas on the right hand side of 
eq.~\ref{chainmap}, the 
differential forms will always be in order. 

More explicitly, using Stokes' theorem for $\pi_!$, we have
\begin{align*}
    d\sigma(\omega_0\otimes\cdots\otimes\omega_k) &= 
    d\pi_!ev_k^*(p_0^*\omega_0\wedge\cdots\wedge p_k^*\omega_k) \\
    &= \int_{\Delta^k}ev_k^*d(p_0^*\omega_0\wedge\cdots\wedge p_k^*\omega_k) \\
    &\pm\int_{\partial\Delta^k} ev_k^*(p_0^*\omega_0\wedge\cdots\wedge 
    p_k^*\omega_k)|_{\partial\Delta^k}.
\end{align*}
The first term, where the $d$ moves inside the integral, matches up with 
$\sigma$ applied to the term (\ref{l1}) in the Hochschild differential.
Similarly, by examining the behavior of $ev_k$ along each of the faces 
$\Delta^{k-1}\subset\Delta^k$ one can check that the integral over the boundary 
is equal to $\sigma$ applied to terms (\ref{l2}) and (\ref{l3}) of the 
Hochschild differential. The key point, however, is that in the integral along 
the last face ($t_k=0$) we need to commute the $p_k^*\omega_k$ all the way to
the left in order to obtain the term with $\omega_k\wedge\omega_0$ in 
(\ref{l3}). Hence we are crucially using the
strict (graded) commutativity of de Rham forms.


\end{document}

